--- 
bookdown::gitbook:
  includes:
      in_header: header.html
---

# Review of R Skills 

```{r setup, include=FALSE}
# Add a common class name for every chunks
knitr::opts_chunk$set(
  echo = TRUE)
```

This part contains two optional vignettes that will help you brush up your basic R programming skills and get a head-start on R graphics.

- [Basic R Programming](#basic-r)
- [R Graphics](#r-graphics)

Optional, advanced topics are presented here:

- [Version Control with Github](#github)
- [Further R Resources](#resources)



## Basic R Programming {#basic-r}

```{r}
rmd_file <- paste0(here::here(), "/vignettes/", "Week0_BasicR.Rmd")
yml_metadata <- rmarkdown::yaml_front_matter(rmd_file)
cat(yml_metadata$author)
```


```{r child=paste0(here::here(), "/vignettes/", "Week0_BasicR.Rmd"), echo=TRUE}
```

## R Graphics {#r-graphics}

```{r}
rmd_file <- paste0(here::here(), "/vignettes/", "Week0_Graphics.Rmd")
yml_metadata <- rmarkdown::yaml_front_matter(rmd_file)
cat(yml_metadata$author)
```

```{r child=paste0(here::here(), "/vignettes/", "Week0_Graphics.Rmd"), echo=TRUE}
```

## Version Control with Github {#github}

### 1. External Github tutorials

- Excellent tutorial: [Happy Git and Github for the useR](https://happygitwithr.com/)
- How to collaborate with Github: [The Ultimate Github Collaboration Guide](https://medium.com/@jonathanmines/the-ultimate-github-collaboration-guide-df816e98fb67)

### 2. Watch course video: Version Control 101

Note: the video mentions a worked example. This has been replaced by the external tutorials listed above.

- External link: [Week 0 video](http://sho.co/19EFD)
- Transcript: [Download transcript](https://raw.githubusercontent.com/hhwagner1/DGS_LG_Labs/master/transcripts/Week0_script.pdf)

Embedded video:

<iframe width="800" height="513" src="http://sho.co/embed/19EFD" frameborder="0" allowfullscreen></iframe>


### 3. Preview slides

[Download]("https://github.com/hhwagner1/DGS_LG_Labs/raw/master/docs/Video_slides/Week0_Slides.pdf")


```{r echo=FALSE, fig.height=48, fig.width=8, message=FALSE}
library(cowplot)
library(ggplot2)

Path=paste0(here::here(), "/downloads/Week0_Slides/")
files <- list.files(Path)

p1 <- ggdraw() + draw_image(paste0(Path, files)[1], scale = 0.9)
p2 <- ggdraw() + draw_image(paste0(Path, files)[2], scale = 0.9)

Plots <- lapply(files, function(j) ggdraw() + draw_image(paste0(Path, j), scale = 0.9) +
                  theme(plot.margin = unit(c(0,0,0,0), "cm"), 
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5)))

plot_grid(plotlist=Plots, ncol=1)
```

## Further R resources {#resources}

Links to some excellent external resources:

- [Applied Population Genetics](https://dyerlab.github.io/applied_population_genetics/index.html)  bz Rodney Dyer
- [Efficient R Programming](https://csgillespie.github.io/efficientR/)  by Colin Gillespie and Robin Lovelace







