--- 
bookdown::gitbook:
  includes:
      in_header: header.html
---

# Review of R Skills 

```{r setup, include=FALSE}
# Add a common class name for every chunks
knitr::opts_chunk$set(
  echo = TRUE)
```

This part contains two optional vignettes that will help you brush up your basic R programming skills and get a head-start on R graphics.

- [Basic R Programming](#basic-r)
- [R Graphics](#r-graphics)
- [Further R Resources](#resources)



## Basic R Programming {#basic-r}

```{r echo=FALSE, results = 'asis'}
rmd_file <- paste0(here::here(), "/vignettes/", "Week0_BasicR.Rmd")
yml_metadata <- rmarkdown::yaml_front_matter(rmd_file)
cat(yml_metadata$author)
```


```{r child=paste0(here::here(), "/vignettes/", "Week0_BasicR.Rmd"), echo=TRUE}
```

## R Graphics {#r-graphics}

```{r echo=FALSE, results = 'asis'}
rmd_file <- paste0(here::here(), "/vignettes/", "Week0_Graphics.Rmd")
yml_metadata <- rmarkdown::yaml_front_matter(rmd_file)
cat(yml_metadata$author)
```

```{r child=paste0(here::here(), "/vignettes/", "Week0_Graphics.Rmd"), echo=TRUE}
```


## Further R resources {#resources}

Links to some excellent external resources:

- [Applied Population Genetics](https://dyerlab.github.io/applied_population_genetics/index.html)  bz Rodney Dyer
- [Efficient R Programming](https://csgillespie.github.io/efficientR/)  by Colin Gillespie and Robin Lovelace







