# (PART\*) Basic Topics {-}
# Week 1: Importing Genetic Data {#Week1}


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse=TRUE)
```


In this first lab of the course, we will explore different ways of importing genetic data into R. Along the way, we will learn about data models in R and how to avoid common errors. 

## View Course Video{#video_1a}


<iframe width="800" height="513" src="https://sho.co/embed/19DCV" frameborder="0" allowfullscreen></iframe>


### Preview Slides

[Download]("https://github.com/hhwagner1/DGS_LG_Labs/raw/master/docs/Video_slides/Week1_Slides.pdf")


```{r echo=FALSE, fig.height=42, fig.width=8, message=FALSE}
library(cowplot)
library(ggplot2)

Path=paste0(here::here(), "/downloads/Week1_Slides/Week1_Slides/")
files <- list.files(Path)

p1 <- ggdraw() + draw_image(paste0(Path, files)[1], scale = 0.9)
p2 <- ggdraw() + draw_image(paste0(Path, files)[2], scale = 0.9)

Plots <- lapply(files, function(j) ggdraw() + draw_image(paste0(Path, j), scale = 0.9) +
                  theme(plot.margin = unit(c(0,0,0,0), "cm"), 
                        panel.border = element_rect(colour = "black", fill=NA, size=0.5)))

plot_grid(plotlist=Plots, ncol=1)
```

## Interactive Tutorial 1{#tutorial_1}

### Instructions

#### a) Goal: ...

#### b) How to access tutorials:

#### c) How to complete tutorial:

#### d) How to submit answers (participating institutions only):


### List of R commands used

```{r echo=FALSE}
library(kableExtra)
Table <- readRDS(paste0(here::here(), "/output/table_list.rds"))[[1]]
Table %>% kable() %>% 
  kable_styling(bootstrap_options = c("bordered", "striped", "condensed", "responsive")) %>%
  kable_styling(fixed_thead = T, full_width=F) 
```	


## Worked Example{#WE_1}

```{r child=paste0(here::here(), "/vignettes/", "Week1_vignette.Rmd"), echo=TRUE}
```


## Bonus: Importing SNP data {#bonus_1a}

