--- 
title: "Landscape Genetic Data Analysis with R"
author: "Editor: Helene Wagner (University of Toronto)"
date: "`r Sys.Date()`"
output:
  bookdown::gitbook:
    includes:
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
github-repo: hhwagner1/LandGenCourse_book
description: "This is a web-interface to the teaching materials for the lab course 'Landscape Genetic Data Analysis with R' associated with the distributed graduate course 'DGS Landscape Genetics'. The output format is bookdown::gitbook."


---
# (PART\*) Getting Started {-}
# Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This is a web-interface to the teaching materials for the lab course 'Landscape Genetic Data Analysis with R' associated with the distributed graduate course  ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website").

The Landscape Genetics Distributed Graduate Seminar (DGS) is an international collaboration that provides a unique opportunity for interdisciplinary graduate training. The course draws on experts from around the world to deliver an in-depth introduction and overview of the field of landscape genetics. The course caters to students in both basic and applied ecology, conservation/population genetics, landscape ecology and conservation biology. Every other year, several hundred students, post-docs and faculty from around the world participate in this course. For more information about the course, and to sign up to be notified when registration opens, please visit the course website: 

Link to [DGS Landscape Genetics](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website")

The online book compiles the teaching materials for the optional computer lab component of the DGS Landscape Genetics. The materials included in this online resource are also included in the R package `LandGenCourse` available on [Github](https://github.com/hhwagner1/LandGenCourse "github repository").   


Next sections:

- [How to use this Book](#how-to-use)
- [List of R Packages by Vignette](#list-of-packages)



## How to use this Book

### 1. Book Structure

This book has weekly chapters that correspond to course modules, with three parts:

#### a) Getting Started 
  - Review of R Skills: check whether you need to build or brush up your R skills before starting the course:
      - [Basic R Programming](#basic-r): introduction to R objects and functions. **Prerequisite**.
      - [R Graphics](#r-graphics): learn to create figures with base R and with `ggplot2`. Optional.
      
      
#### b) Basic Topics
  - These 8 weekly modules are streamlined to build the necessary R skills and brush up statistics knowledge. Best complete these in sequence.
  - Each module has the following components:
      - Video: introduces the R and stats topics
      - Interactive Tutorial: swirl course to practice R programming
      - Worked Example: worked example by the weekly experts from the ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website") course.
      - Bonus Materials: some weeks include bonus vignettes with optional advanced topics.
      
      
#### c) Advanced Topics
  - These weekly modules build on the skills developed in Basic Topics. You may pick and choose from the Advanced Topics according to your interests.
  - Each weekly modules contains:
      - Worked Example: worked example by the weekly experts from the ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website") course.
      - Bonus Materials: some weeks include bonus vignettes with optional advanced topics.

### 2. Find what is relevant for you

#### a) How to use the labs {#how-to-use} 

Weeks 1 - 8:

- **Beginners**:   
    - watch video 
    - do tutorial to build basic R programming skills
    - read worked example, focus on content
    
- **Intermediate**:   
    - watch video 
    - check weekly tutorial functions: do tutorial to brush up?
    - understand worked example, focus on content and code
    - do R exercise to practice coding
    
- **Advanced**:   
    - check video slides: watch video to brush up on concepts?
    - R exercise? 
    - adapt worked example to own data

**By Week 9**: you will be at least at ‘intermediate’ level if not a pro!


#### b) Check contents

- **Videos**: Check first weekly slide, browse slides for each week
- **Interactive tutorials**: check weekly list of commands for each chapter
- **Worked examples**: check [List of R Packages by Vignette](#list-of-packages); check introduction section for each worked example (or bonus vignette) 

### 3. Course R package 'LandGenCourse'

#### a) Practice good R hygiene

Please update or install the following before installing 'LandGenCourse':

**Windows**:

- R: https://cran.r-project.org/
- RStudio: https://www.rstudio.com/products/rstudio/download/#download
- If asked to install Rtools during package installation: accept

**Mac**: please follow the order below exactly!

- Xquartz: https://www.xquartz.org/ (re-install after each MacOS upgrade)
- R: https://cran.r-project.org/
- RStudio: https://www.rstudio.com/products/rstudio/download/#download
- If asked to install Command Line Tools during package installation: accept
- If asked which packages to install, select 'All'.
- If needed, manually install Command Line Tools. Instructions:
http://osxdaily.com/2014/02/12/install-command-line-tools-mac-os-x/

#### b) How to install (or update) 'LandGenCourse'

```{r message=FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("hhwagner1/LandGenCourse")
library(LandGenCourse)
```

Hints:

- Make sure you load the package (`library(LandGenCourse)`) after installing it!
- Check whether the add-ins 0 - 4 are available: in the RStudio menu, click on the drop-down menu `Addins`. 
- If the add-ins 0 - 4 don't appear, rerun the code above (install and load package `LandGenCourse`). Sometimes this seems to be necessary.

#### c) How to install dependencies

The previous step only installed the absolutely required dependencies (i.e., R packages that `LandGenCourse` needs so that it can be installed). However, the weekly chapters will require additional R packages. There are two ways to install them:

**Option 1: Install as you go**

- Newer versions of RStudio will warn you when a R notebook (`.Rmd`) that you opened requires R packages that are not installed. 
- The warning contains a link `Install`, click on it to install the missing packages.

**Option 2: Bulk install**

- Use the Addin `0. Install Packages` to bulk install most or all packages needed to run the worked examples.
- Simply click on the add-in `0. Install Packages` (alternatively, you could run this code: `installDGS()`)
- If asked whether to install some package from source (`Do you want to install from sources the package which needs compilation? (Yes/no/cancel)`), you may enter: `no` (this is faster)
- If the installation stops with an error `API rate limit exceeded`, the best thing to do is to wait 30 min and run the Addin `0. Install Packages` again. Don't worry, this won't start the installation process again, it will resume where it broke off. 
- If you often install packages from Github, you may want to follow up on the advice printed with the error message:
    - Use `usethis::create_github_token()` to create a Personal Access Token.
    - Use `usethis::edit_r_environ()` and add the token as `GITHUB_PAT`.
- If you do so, the second line above will open the file `.Renviron` in RStudio. Enter `GITHUB_PAT="myPAT"` on the last line (replace `myPAT` by the PAT you generated using the first line). Make sure to include an empty line after it! Save the file and restart R. 

#### d) How to use the R package `LandGenCourse`

The package installs four more Addins in RStudio. Each will provide you with some dropdown menu choices.

- **1. Watch Course Video**: opens a video resource from course "Landscape Genetic Data Analysis with R".
- **2. Start Tutorial**: installs swirl course "Landscape_Genetics_R_Course" and prints instructions.
- **3. Choose Worked Example**: opens vignette file (.html, .Rmd, or .R) with a worked example from course "Landscape Genetic Data Analysis with R".
- **4. Open Cheat Sheet**: opens selected R cheat sheet.

#### e) Video instructions for beginners

This video walks through the process of installing devtools, the course package, and using the RStudio Add-Ins.
<a href="https://www.dropbox.com/s/598kwim7x09m47t/Intro_LandGenCourse_small.mp4?dl=0" target="_blank">Intro_LandGenCourse_small.mp4</a>


## List of R Packages by Vignette {#list-of-packages} 

Scroll through the list to find which R packages are used in which vignette (i.e., weekly worked example or bonus vignette). This may be helpful for finding relevant materials if you are interested in a specific type of analysis.

Notes: 

- 'B' and 'G' refer to the [Review of R Skills](#review-of-r-skills) section (B = [Basic R](#basic-r), G =  [Graphics](#r-graphics))
- Lowercase letters refer to bonus vignettes. E.g., 2a is the (first) bonus vignette of Week 2. 


```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE}

library(kableExtra)
Table <- readRDS(paste0(here::here(), "/output/Full.rds"))
Table %>% kable() %>% 
  kable_styling(bootstrap_options = c("bordered", "striped", "condensed", "responsive")) %>%
  kable_styling(fixed_thead = T, full_width=F, font_size = 10) %>%
       column_spec(1, border_left = T) %>% column_spec(1, border_right = T)  %>%
       column_spec(c(1,3,13, ncol(Table)+1), border_right = T, width=2) %>% 
       column_spec(c(2,4:12,14:ncol(Table)), border_right = T)
```



```{r echo=FALSE}

library(kableExtra)
Table <- readRDS(paste0(here::here(), "/output/Full.rds"))
Table %>% kable() %>% kable_paper() %>% scroll_box(width = "100%", height = "200px") %>%
  kable_styling(bootstrap_options = c("bordered", "striped", "condensed", "responsive")) %>%
  kable_styling(fixed_thead = T, full_width=F, font_size = 12)
```


