--- 
title: "Landscape Genetic Data Analysis with R"
author: "Editor: Helene Wagner (University of Toronto)"
date: "`r Sys.Date()`"
output:
  bookdown::gitbook:
    includes:
      in_header: header.html
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib]
biblio-style: apalike
link-citations: yes
github-repo: hhwagner1/LandGenCourse_book
description: "This is a web-interface to the teaching materials for the lab course 'Landscape Genetic Data Analysis with R' associated with the distributed graduate course 'DGS Landscape Genetics'. The output format is bookdown::gitbook."


---
# (PART\*) Getting Started {-}
# Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



This is a web-interface to the teaching materials for the lab course 'Landscape Genetic Data Analysis with R' associated with the distributed graduate course  ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website").

All teaching materials are included in the R package `LandGenCourse` available on [Github](https://github.com/hhwagner1/LandGenCourse "github repository") 

**Code visiblity**: use the `Code` button to show or hide all R code, either globally or by chunk.

## How to use this Book

### 1. Book Structure

This book has weekly chapters that correspond to course modules, with three parts:

#### a) Getting Started 
  - Review of R Skills: check whether you need to build or brush up your R skills before starting the course:
      - Basic R Programming: introduction to R objects and functions. **Prerequisite**.
      - R Graphics: learn to create figures with base R and with `ggplot2`. Optional.
      
#### b) Basic Topics
  - These 8 weekly modules are streamlined to build the necessary R skills and brush up statistics knowledge. Best complete these in sequence.
  - Each module has the following components:
      - Video: introduces the R and stats topics
      - Interactive Tutorial: swirl course to practice R programming
      - Worked Example: worked example by the weekly experts from the ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website") course.
      - Bonus Materials: some weeks include bonus vignettes with optional advanced topics.
      
#### c) Advanced Topics
  - These weekly modules build on the skills developed in Basic Topics. You may pick and choose from the Advanced Topics according to your interests.
  - Each weekly modules contains:
      - Worked Example: worked example by the weekly experts from the ['DGS Landscape Genetics'](https://sites.google.com/site/landscapegeneticscourse/ "DGS public website") course.
      - Bonus Materials: some weeks include bonus vignettes with optional advanced topics.

### 2. Find what is relevant for you

#### a) How to use the labs 

Weeks 1 - 8:

- **Beginners**:   watch video -> do tutorial -> read WE
- **Intermediate**:   watch video -> tutorial? -> understand WE -> do R exercise
- **Advanced**:   check video slides -> R exercise? -> adapt WE to own data

**By Week 9**: you will be at least at ‘intermediate’ if not a pro!

#### b) Check contents

- **Videos**: Check first weekly slide, browse slides for each week
- **Interactive tutorials**: check weekly list of commands for each chapter
- **Worked examples**: check list of packages by vignette (below), check introduction section for each worked example (or bonus vignette) 

### 3. Course R package `LandGenCourse`

#### a) How to install (or update)
```{r}
if (!require("devtools")) install.packages("devtools")
devtools::install_github("hhwagner1/LandGenCourse")
library(LandGenCourse)
```

#### b) How to use the R package `LandGenCourse`

The package installs four Add-ins in RStudio. Each will provide you with some dropdown menu choices.

- **Watch Course Video**: opens a video resource from course "Landscape Genetic Data Analysis with R".
- **Start Tutorial**: installs swirl course "Landscape_Genetics_R_Course" and prints instructions.
- **Choose Worked Example**: opens vignette file (.html, .Rmd, or .R) with a worked example from course "Landscape Genetic Data Analysis with R".
- **Open Cheat Sheet**: opens selected R cheat sheet.

#### c) Video instructions for beginners
This video walks through the process of installing devtools, the course package, and using the RStudio Add-Ins.
<a href="https://www.dropbox.com/s/598kwim7x09m47t/Intro_LandGenCourse_small.mp4?dl=0" target="_blank">Intro_LandGenCourse_small.mp4</a>


## List of Packages by Vignette

Note: lowercase letters refer to bonus vignettes. E.g., 2a is the (first) bonus vignette of Week 2. 

```{r echo=FALSE, message=FALSE, warning=FALSE, include=FALSE}
library(kableExtra)
Table <- readRDS(paste0(here::here(), "/output/Full.rds"))
Table %>% kable() %>% 
  kable_styling(bootstrap_options = c("bordered", "striped", "condensed", "responsive")) %>%
  kable_styling(fixed_thead = T, full_width=F, font_size = 10) %>%
       column_spec(1, border_left = T) %>% column_spec(1, border_right = T)  %>%
       column_spec(c(1,3,13, ncol(Table)+1), border_right = T, width=2) %>% 
       column_spec(c(2,4:12,14:ncol(Table)), border_right = T)
```


```{r eval=FALSE}
library(kableExtra)
Table %>% kable() %>% kable_paper() %>% scroll_box(width = "100%", height = "200px") %>%
  kable_styling(bootstrap_options = c("bordered", "striped", "condensed", "responsive")) %>%
  kable_styling(fixed_thead = T, full_width=F, font_size = 12)
```


