---
title: "My bookdown workflow"
output: html_notebook
---

Packages

```{r}
library(xfun)
library(magick)
library(servr)
library(rsconnect)
```

## Import and prepare files from `LandGenCourse`

```{r download}
Path <- here::here()
if(!file.exists(file.path(Path, "data", "Wetlands.csv")))
{
  d = "https://spatialr.s3.us-west-2.amazonaws.com/Gravity/data.zip"
  download.file(d, destfile=file.path(Path, "data.zip"), mode="wb")
  unzip(file.path(Path, "data.zip"))
  file.remove(file.path(Path, "data.zip"))
}
```

Import all Rmd and other (png) files from vignettes, replace old files

```{r}
myDir <- unlist(strsplit(here::here(), '/'))
myDir[length(myDir)] <- "LandGenCourse"
Path <- paste0(myDir, collapse = '/')

list.of.files <- list.files(paste0(Path, "/vignettes"))
file.copy(paste0(Path, "/vignettes/", list.of.files), 
          paste0(here::here(), "/vignettes"), overwrite=TRUE)
dir(paste0(here::here(), "/vignettes"))

```

Increase header level by 1

```{r}
gsub_ext(ext="Rmd", "# 1.", "## 1.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 2.", "## 2.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 3.", "## 3.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 4.", "## 4.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 5.", "## 5.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 6.", "## 6.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 7.", "## 7.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 8.", "## 8.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 9.", "## 9.",  dir = paste0(here::here(), "/vignettes"))

gsub_ext(ext="Rmd", "# a.", "## a.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# b.", "## b.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# c.", "## c.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# d.", "## d.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# e.", "## e.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# f.", "## f.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# g.", "## g.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# h.", "## h.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# i.", "## i.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# j.", "## j.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# k.", "## k.",  dir = paste0(here::here(), "/vignettes"))

```

Make R Exercises a separate sub-chapter (for Weeks 1 - 8)

```{r}
## 7. R exercise Week 1 {-}
gsub_ext(ext="Rmd", "### 4. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 5. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 6. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 7. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 8. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 9. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
```

Number R exercises


```{r eval=FALSE, include=FALSE}
## 7. R exercise Week 1 {-}
gsub_ext(ext="Rmd", "## R exercise Week 1 \\{-}", "## R exercise Week 1",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 2 \\{-}", "## R Exercise Week 2",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 3 \\{-}", "## R Exercise Week 3",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 4 \\{-}", "## R Exercise Week 4",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 5 \\{-}", "## R Exercise Week 5",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 6 \\{-}", "## R Exercise Week 6",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 7 \\{-}", "## R Exercise Week 7",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "## R Exercise Week 8 \\{-}", "## R Exercise Week 8",  dir = paste0(here::here(), "/vignettes"))
```

```{r}
gsub_ext(ext="Rmd", "WE9_Fig1.png", paste0(here::here(), "/vignettes/WE9_Fig1.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE9_Fig2.png", paste0(here::here(), "/vignettes/WE9_Fig2.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE12_Fig1.png", paste0(here::here(), "/vignettes/WE12_Fig1.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE13_Fig1.PNG", paste0(here::here(), "/vignettes/WE13_Fig1.PNG"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "radish_tutorial_fig1A.png", paste0(here::here(), "/vignettes/radish_tutorial_fig1A.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "radish_tutorial_fig1B.png", paste0(here::here(), "/vignettes/radish_tutorial_fig1B.png"),  dir = paste0(here::here(), "/vignettes"))
```


Create list of functions and packages: source file "ListOfPackages.Rmd" 

```{r message=FALSE, include=FALSE}
library(knitr)
source(purl(paste0(here::here(), "/ListOfPackages.Rmd"), output = tempfile()))
```


Import tables of R commands of tutorials from Word file


```{r message=FALSE}
library(officer)
library(dplyr)

myDir <- unlist(strsplit(here::here(), '/'))
myDir[length(myDir)] <- "LandGenCourse"
Path <- paste0(myDir, collapse = '/')
inFile <- paste0(Path, "/inst/extdata/RCommands.docx")

sample_data <- officer::read_docx(inFile)
content <- docx_summary(sample_data)
paragraphs <- content %>% filter(content_type == "paragraph")
paragraphs$text
content %>% filter(content_type == "table cell")
table_cells <- content %>% filter(content_type == "table cell")
table_data <- table_cells %>% filter(!is_header) %>% dplyr::select(row_id, cell_id, text)
 
# split data into individual columns
splits <- split(table_data, table_data$cell_id)
splits <- lapply(splits, function(x) x$text)
 
# combine columns back together in wide format
table_result <- bind_cols(splits)


table_result  <- table_result %>% mutate(Week=cumsum(table_result[,3]=="Comments"))
table_list <- split(table_result, table_result$Week)

getNames <- function(ls)
{
  names(ls) <- as.character(ls[1,])
  ls <- ls[-1,] 
  ls[,1:2]
}

table_list <- lapply(table_list, getNames)
saveRDS(table_list, paste0(here::here(), "/output/table_list.rds"))
```

## Preview chapter


```{r}
#source(knitr::purl(paste0(here::here(), "/vignettes/Week8_bonus_vignette.Rmd")))

#bookdown::preview_chapter("08-Week08.Rmd")

#bookdown::render_book(input="index.Rmd", preview=TRUE)
```



## Compile book

```{r message=FALSE, include=FALSE}
bookdown:::serve_book()
```


## NOT NEEDED? API for accessing RStudio Connect (first time in session)

To put the information into the .Renviron file, paste the following lines into the file:

CONNECT_SERVER="https://bookdown.org/"
CONNECT_API_KEY=

```{r eval=FALSE, include=FALSE}
usethis::edit_r_environ()  # This will open the file
```

At the beginning of the session:

```{r eval=FALSE, include=FALSE}
library(httr)

connectServer <- "https://bookdown.org/"

# The initial request in an R session will have no HTTP session cookies.
resp <- httr::GET(connectServer, 
  path = "/content/24/mean",
  query = list(samples = 5),
  add_headers(Authorization = paste("Key", connectAPIKey))
)
# ...

# Later requests retain cookies set by the previous request.
resp <- httr::GET(connectServer, 
  path = "/content/24/mean",
  query = list(samples = 10),
  add_headers(Authorization = paste("Key", connectAPIKey))
)
# ...
```


## Push to bookdown.org

```{r}
bookdown::publish_book()
```

## Clean up

Check files to be deleted

```{r}
bookdown::clean_book(FALSE)
```

Delete them

```{r}
bookdown::clean_book(TRUE)
```

Delete copies of Rmd files from LandGenCourse

```{r}
unlink(paste0(here::here(), "/vignettes/", list.of.files), recursive = FALSE)
dir(paste0(here::here(), "/vignettes"))
```

