---
title: "My bookdown workflow"
output: html_notebook
---

Packages

```{r}
library(xfun)
library(magick)
```

## Import and prepare files from `LandGenCourse`

Import all Rmd and other (png) files from vignettes, replace old files

```{r}
#Mac:
#Path <- "/Users/helene/Desktop/R_github_projects/LandGenCourse/vignettes/" 
#Windows:
Path <- "C:/Users/wagnerh1/Desktop/LandGenCourse/vignettes/" # Laptop
#list.of.files <- list.files(Path, pattern="Rmd")
list.of.files <- list.files(Path)
file.copy(paste0(Path, list.of.files), paste0(here::here(), "/vignettes"), overwrite=TRUE)
dir(paste0(here::here(), "/vignettes"))

```

Increase header level by 1

```{r}
gsub_ext(ext="Rmd", "# 1.", "## 1.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 2.", "## 2.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 3.", "## 3.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 4.", "## 4.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 5.", "## 5.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 6.", "## 6.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 7.", "## 7.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 8.", "## 8.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# 9.", "## 9.",  dir = paste0(here::here(), "/vignettes"))

gsub_ext(ext="Rmd", "# a.", "## a.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# b.", "## b.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# c.", "## c.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# d.", "## d.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# e.", "## e.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# f.", "## f.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# g.", "## g.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# h.", "## h.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# i.", "## i.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# j.", "## j.",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "# k.", "## k.",  dir = paste0(here::here(), "/vignettes"))

```
Make R Exercises a separate sub-chapter (for Weeks 1 - 8)

```{r}
gsub_ext(ext="Rmd", "### 4. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 5. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 6. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 7. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 8. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "### 9. R ", "## R ",  dir = paste0(here::here(), "/vignettes"))
```

In some chapters (1 - 3?), put slot names in text into quotes
```{r}
gsub_ext(ext="Rmd", " @C", " `@C`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @E", " `@E`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @S", " `@S`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @XY", " `@XY`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @all.names", " `@all.names`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @bbox", " `@bbox`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @coords", " `@coords`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @coords.nrs", " `@coords.nrs`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @data", " `@data`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @hierarchy", " `@hierarchy`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @lines", " `@lines`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @loc.fac", " `@loc.fac`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @loc.n.all", " `@loc.n.all`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @other", " `@other`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @ploidy", " `@ploidy`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @pop", " `@pop`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @proj4string", " `@proj4string`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @strata", " `@strata`",  
         dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @tab", " `@tab`",  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", " @type", " `@type`",  dir = paste0(here::here(), "/vignettes"))
```

```{r}
gsub_ext(ext="Rmd", "WE9_Fig1.png", paste0(here::here(), "/vignettes/WE9_Fig1.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE9_Fig2.png", paste0(here::here(), "/vignettes/WE9_Fig2.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE12_Fig1.png", paste0(here::here(), "/vignettes/WE12_Fig1.png"),  dir = paste0(here::here(), "/vignettes"))
gsub_ext(ext="Rmd", "WE13_Fig1.PNG", paste0(here::here(), "/vignettes/WE13_Fig1.PNG"),  dir = paste0(here::here(), "/vignettes"))
```


Create list of functions and packages: source file "ListOfPackages.Rmd" 

```{r message=FALSE, include=FALSE}
library(knitr)
source(purl(paste0(here::here(), "/ListOfPackages.Rmd"), output = tempfile()))
```


Import tables of R commands of tutorials from Word file


```{r message=FALSE}
library(officer)
library(dplyr)

# Mac:
#inFile <- "/Users/helene/Desktop/R_github_projects/LandGenCourse/inst/extdata/RCommands.docx"
# Windows:
inFile <- "C:/Users/wagnerh1/Desktop/LandGenCourse/inst/extdata/RCommands.docx"

sample_data <- officer::read_docx(inFile)
content <- docx_summary(sample_data)
paragraphs <- content %>% filter(content_type == "paragraph")
paragraphs$text
content %>% filter(content_type == "table cell")
table_cells <- content %>% filter(content_type == "table cell")
table_data <- table_cells %>% filter(!is_header) %>% dplyr::select(row_id, cell_id, text)
 
# split data into individual columns
splits <- split(table_data, table_data$cell_id)
splits <- lapply(splits, function(x) x$text)
 
# combine columns back together in wide format
table_result <- bind_cols(splits)


table_result  <- table_result %>% mutate(Week=cumsum(table_result[,3]=="Comments"))
table_list <- split(table_result, table_result$Week)

getNames <- function(ls)
{
  names(ls) <- as.character(ls[1,])
  ls <- ls[-1,] 
  ls[,1:2]
}

table_list <- lapply(table_list, getNames)
saveRDS(table_list, paste0(here::here(), "/output/table_list.rds"))
```



## Preview chapter

NOTE: for some reason, chapter 8 (bonus vignette) needs to be precompiled before serving the entire book, may have to do with paths.

May need to run all chunks in Week 8 bonus vignette before rendering the chapter.

```{r}
source(knitr::purl(paste0(here::here(), "/vignettes/Week8_bonus_vignette.Rmd")))

bookdown::preview_chapter("08-Week08.Rmd")

#bookdown::render_book(input="index.Rmd", preview=TRUE)
```


## Compile book

```{r message=FALSE, include=FALSE}
bookdown:::serve_book()
```


## NOT NEEDED? API for accessing RStudio Connect (first time in session)

To put the information into the .Renviron file, paste the following lines into the file:

CONNECT_SERVER="https://bookdown.org/"
CONNECT_API_KEY=

```{r}
usethis::edit_r_environ()  # This will open the file
```

At the beginning of the session:

```{r}
library(httr)

connectServer <- "https://bookdown.org/"
#connectAPIKey <- 

#connectServer <- Sys.getenv("CONNECT_SERVER")
#connectAPIKey <- Sys.getenv("CONNECT_API_KEY")

# The initial request in an R session will have no HTTP session cookies.
resp <- httr::GET(connectServer, 
  path = "/content/24/mean",
  query = list(samples = 5),
  add_headers(Authorization = paste("Key", connectAPIKey))
)
# ...

# Later requests retain cookies set by the previous request.
resp <- httr::GET(connectServer, 
  path = "/content/24/mean",
  query = list(samples = 10),
  add_headers(Authorization = paste("Key", connectAPIKey))
)
# ...
```


## Push to bookdown.org

```{r}
bookdown::publish_book()
```

## Clean up

Check files to be deleted

```{r}
bookdown::clean_book(FALSE)
```

Delete them
```{r}
bookdown::clean_book(TRUE)
```

Delete copies of Rmd files from LandGenCourse

```{r}
unlink(paste0(here::here(), "/vignettes/", list.of.files), recursive = FALSE)
dir(paste0(here::here(), "/vignettes"))
```

